Estimating duration in the presence of misclassification

### 2024-03-29 cis-perf-new-ll.tex
correct notation

Introducing false negatives means that $O(j)$ is now a random, even if $B_j$ and $E_j$ are known.
Define the relevant testing times for episode $j$ as $\sched'_j = \{ t \in \sched_{i(j)} \ssep r_j^{(b)} \leq t \leq r_j^{(e)} + 1 \}$, let $m_j$ denote the size of this set.
Let $O'(j) = [O(j), \vec{y}_j]^T$ where $\vec{y}_j$ is a binary vector of length $m_j$, with the $l$th element of of $\vec{y}_j$ being the test result at the chronologically $l$th time $t \in \sched'_j$.
$O'(j)$ is the observed data for episode $j$.
Defining analogous variables to \cref{E-perf-test}, let $\set{D}' = \{ \vec{\nu}'_1, \dots, \vec{\nu}'_{N_D} \}$ where $\vec{\nu}'_j \in \set{D}'_j$ if and only if $\vec{\nu}'_j = [\vec{\nu}_j, \vec{y}_j]^T$ could be a detected observation, equivalent to satisfying all the following conditions.
\begin{enumerate}
  \item $\vec{\nu}_j \in \set{D}$.
  \item $\vec{y}_j \in \{0, 1\}^{m_j}$.
  \item The elements of $\vec{y}_j$ corresponding to the tests at times $r_j^{(b)}$ (its first element) and $l_j^{(e)}$ (its penultimate element) are 1.
  \item The element of $\vec{y}_j$ corresponding to the test at time $r_j^{(e)} + 1$ (its last element) is 0.
\end{enumerate}
The final two conditions are due the construction of the intervals as positive and negative tests bounding the beginning and end times of the episode.

>>>>

Introducing false negatives means that $O(j)$ is now a random, even if $B_j$ and $E_j$ are known.
Define the relevant testing times for episode $j$ as $\sched'_j = \{ t \in \sched_{i(j)} \ssep r_j^{(b)} \leq t \leq r_j^{(e)} + 1 \}$, let $m_j$ denote the size of this set.
Let $O'(j) = [O(j), \vec{y}_j]^T$ where $\vec{y}_j$ is a binary vector of length $m_j$, with the $l$th element of of $\vec{y}_j$ being the test result at the chronologically $l$th time $t \in \sched'_j$.
$O'(j)$ is the observed data for episode $j$.

Defining analogous variables to \cref{E-perf-test}, let $\set{D}' = \{ \vec{\nu}'_1, \dots, \vec{\nu}'_{N_{D'}} \}$ where $\vec{\nu}'_k \in \set{D}'_k$ if and only if $\vec{\nu}'_k = [\vec{\nu}_k, \vec{y}_k]^T$ could be a detected observation, equivalent to satisfying all the following conditions.
\begin{enumerate}
  \item $\vec{\nu}_k \in \set{D}$.
  \item $\vec{y}_k \in \{0, 1\}^{m_k}$.
  \item The elements of $\vec{y}_k$ corresponding to the tests at times $r_k^{(b)}$ (its first element) and $l_k^{(e)}$ (its penultimate element) are 1.
  \item The element of $\vec{y}_k$ corresponding to the test at time $r_k^{(e)} + 1$ (its last element) is 0.
\end{enumerate}
The final two conditions are due the construction of the intervals as positive and negative tests bounding the beginning and end times of the episode.
